Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Rewrite deployment scenarios.

\section{Usage scenarios}

The default usage scenario has a single paid App Engine instance, publicly known and usable by anyone,
with software configured to use the public instance by default.
This way has the greatest usability because there is nothing to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to bridge now includes Google and the app operators, not only the ISP and intermediate routers that were there before.
On the other hand, the bridge no longer gets to see users' IP addresses.
In effect, Google and the app become what Tor calls a ``guard node.''
Because Tor is encrypted and integrity-protected, neither Google nor the app operators
are able to read or alter users' communications, but being able to measure packet timings,
for example, is necessary for certain linking attacks.

Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
In this scenario, Google still has a privileged network position,
but the user's traffic is no longer visible to the operators of the public app instance.
% Outgoing HTTP requests include app id? As good as an IP address.

The code that runs on App Engine is very simple.
It just statelessly copies HTTP requests and responses.
Another usage scenario has the App Engine code ported to another language such as PHP,
so that it can be run in ordinary web hosting environments.
What you lose with a PHP app is Google's unblockability;
the censor may find and individually block the domains
This scenario is still interesting because there are so many places
where such an app can be run, with low cost and minimal setup.
Installing a PHP file on a web host environment is easier than setting up a Tor bridge or SOCKS proxy.
The URLs of PHP bridges could be distributed in a way like BridgeDB.

@@

>>>>

@@

\subsection{Other deployment scenarios}

The deployment we envision and have started to implement
uses a single paid App Engine instance, which is publicly known and usable by anyone.
Client software is configured to use this public instance by default.
A preconfigured public instance has great usability advantages
because there is nothing for the user to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to Tor bridge now includes App Engine and the web app operators,
in addition to the ISP and intermediate routers that were there before.
On the other hand, the Tor bridge no longer gets to see users' IP addresses:
all it sees are many connections from the App Engine.
In effect, App Engine and the web app become what Tor calls a ``guard node,''
a privileged relay that takes the first hop in the chain of relays.
Because Tor is encrypted and integrity-protected, neither App Engine nor the app operators
are able to read or alter users' communications, but being on path enables them
to do things like measure packet timing patterns.

Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
In this scenario, Google still has a privileged network position,
but the user's traffic patterns are no longer visible to the operators of a public app instance.
% Outgoing HTTP requests include app id? As good as an IP address.

The code that runs on App Engine is very simple.
It just statelessly copies HTTP requests and responses.
Another possible deployment scenario uses a PHP implementation of the reflector,
deployed on an ordinary web hosting service other than App Engine.
In this scenario, domain fronting is not used;
instead unblockability depends on there being many (individually blockable) PHP reflectors.
In other words, it is roughly the same situation as exists today with Tor bridges,
except that it can be much easier for a volunteer to upload a PHP file to a web host
than to set up Tor bridge or other proxy.
Such PHP bridges could potentially automatically report their own URLs,
which could be distributed using a system like BridgeDB.
